Presentation Materials

### 2017-03-14 San Antonio/presentation_materials.Rmd
added statistics of ai_class to top ten fatal accidents

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
require(dplyr)
knitr::opts_knit$set(root.dir = "~/Git/violation-data-analysis")
```

@@

```{r top 10 fatality}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.deaths <- complete.active.quarters %>% filter(active & year >= 2005) %>% arrange(desc(num.death)) %>% select(mine.name, mine_id, year, quarter, num.death)
head(top.deaths, 10)
```
### Top 10 Causes of Death
```{r top 10 causes of death}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY") %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)
```

@@

```{r upper big branch}
# {r upper big branch, echo=FALSE, fig.show = 'hold', out.width = '49%'}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
# upper.big.branch <- complete.active.quarters %>% filter(mine_id == 4608436 & (year < 2010 | (year == 2010 & quarter < 2))) %>%
#   select(year, quarter, num.days.lost, viol.quantity)
# # ggplot() +
# #   geom_line(data = upper.big.branch, aes(x = year + quarter / 4, y = viol.quantity), color = "red") +
# #   geom_line(data = upper.big.branch, aes(x = year + quarter / 4, y = num.days.lost), color = "green")
# qplot(x=year + quarter / 4, y=viol.quantity, data=upper.big.branch, geom = "line",
#      main = "Upper Big Branch: Number of Quarterly Violations",
#      xlab = "Year", ylab = "Count")

@@

```{r sago}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4608791 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r crandall}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}

yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4201715 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r darby}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
# darby.mine <- complete.active.quarters %>% filter(mine_id == 1518185 & (year < 2006 | (year == 2006 & quarter < 2))) %>%
#   select(year, quarter, num.days.lost, viol.quantity)
# qplot(x=year + quarter / 4, y=viol.quantity, data=darby.mine, geom = "line",
#      main = "Darby Mine No. 1: Number of Quarterly Violations",
#      xlab = "Year", ylab = "Count")

@@

```{r gibson}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
# gibson.mine <- complete.active.quarters %>% filter(mine_id == 1202215 & (year < 2007 | (year == 2007 & quarter < 3))) %>%
#   select(year, quarter, num.days.lost, viol.quantity)
# qplot(x=year + quarter / 4, y=viol.quantity, data=gibson.mine, geom = "line",
#      main = "Gibson Mine: Number of Quarterly Violations",
#      xlab = "Year", ylab = "Count")

@@

```{r Revenue Mine}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 503528 & year < 2013) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r Dotiki Mine}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1502132 & year < 2010) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r p-3}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1510212 & year < 2005) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r D-14}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1517165 & year < 2005) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r equality}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1519344 & year < 2011) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

Among the top 10 mine-quarters based on number of days lost,
```{r top 10 days lost}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.days.lost <- complete.active.quarters %>% filter(active) %>% arrange(desc(num.days.lost)) %>% select(mine.name, year, quarter, num.days.lost)
head(top.days.lost, 10)
```
the "American Coal Company New Era Mine" take 5 spots.
Let's take a look at its second quarter of 2005:
```{r new era}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc
    #ai_occ_desc 
    #ai_narr
    ) 
head(new.era)
```
In particular, the top accident was:
```{r new era accident 1}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era.top.accidents <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc,
    ai_occ_desc, 
    ai_narr
    ) 
print(as.character(new.era.top.accidents$ai_narr[1]))
```
and the second to top accident was:
```{r new era, accident 2}
if(!exists("new.era.top.accidents")){
 if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era.top.accidents <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc,
    ai_occ_desc, 
    ai_narr
    )  
}
print(as.character(new.era.top.accidents$ai_narr[2]))
```

@@

### Lognormal Distribution

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
require(dplyr)
require(ggplot2)
knitr::opts_knit$set(root.dir = "~/Git/violation-data-analysis")
```

@@

```{r top 10 fatality}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.deaths <- complete.active.quarters %>% filter(active & year >= 2005) %>% arrange(desc(num.death)) %>% select(mine.name, mine_id, year, quarter, num.death)
head(top.deaths, 10)
```
### Top 10 Causes of Death Since 2005
```{r top 10 causes of death}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & cal_yr >= 2005) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)
```

@@

```{r upper big branch}
# {r upper big branch, echo=FALSE, fig.show = 'hold', out.width = '49%'}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2010 & cal_qtr == 2 & mine_id ==4608436) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
# upper.big.branch <- complete.active.quarters %>% filter(mine_id == 4608436 & (year < 2010 | (year == 2010 & quarter < 2))) %>%
#   select(year, quarter, num.days.lost, viol.quantity)
# # ggplot() +
# #   geom_line(data = upper.big.branch, aes(x = year + quarter / 4, y = viol.quantity), color = "red") +
# #   geom_line(data = upper.big.branch, aes(x = year + quarter / 4, y = num.days.lost), color = "green")
# qplot(x=year + quarter / 4, y=viol.quantity, data=upper.big.branch, geom = "line",
#      main = "Upper Big Branch: Number of Quarterly Violations",
#      xlab = "Year", ylab = "Count")

@@

```{r sago}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2006 & cal_qtr == 1 & mine_id ==4608791) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4608791 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r crandall}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2007 & cal_qtr == 3 & mine_id ==4201715) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4201715 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r darby}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2006 & cal_qtr == 2 & mine_id ==1518185) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
# darby.mine <- complete.active.quarters %>% filter(mine_id == 1518185 & (year < 2006 | (year == 2006 & quarter < 2))) %>%
#   select(year, quarter, num.days.lost, viol.quantity)
# qplot(x=year + quarter / 4, y=viol.quantity, data=darby.mine, geom = "line",
#      main = "Darby Mine No. 1: Number of Quarterly Violations",
#      xlab = "Year", ylab = "Count")

@@

```{r gibson}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2007 & cal_qtr == 3 & mine_id ==1202215) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
# gibson.mine <- complete.active.quarters %>% filter(mine_id == 1202215 & (year < 2007 | (year == 2007 & quarter < 3))) %>%
#   select(year, quarter, num.days.lost, viol.quantity)
# qplot(x=year + quarter / 4, y=viol.quantity, data=gibson.mine, geom = "line",
#      main = "Gibson Mine: Number of Quarterly Violations",
#      xlab = "Year", ylab = "Count")

@@

```{r Revenue Mine}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2013 & cal_qtr == 4 & mine_id ==503528) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 503528 & year < 2013) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r Dotiki Mine}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2010 & cal_qtr == 2 & mine_id ==1502132) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1502132 & year < 2010) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r p-3}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2005 & cal_qtr == 3 & mine_id ==1510212) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1510212 & year < 2005) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r D-14}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2005 & cal_qtr == 3 & mine_id ==1517165) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1517165 & year < 2005) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

```{r equality}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
fatal.accidents <- accidents %>% 
  filter(inj_degr_desc == "FATALITY" & 
           cal_yr == 2011 & cal_qtr == 4 & mine_id ==1519344) %>%
  group_by(ai_class_desc) %>%
  summarise(count = n()
            ) %>%
  arrange(desc(count))
head(fatal.accidents, 10)

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1519344 & year < 2011) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

Among the top 10 mine-quarters based on number of days lost,
```{r top 10 days lost}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
top.days.lost <- complete.active.quarters %>% filter(active) %>% arrange(desc(num.days.lost)) %>% select(mine.name, year, quarter, num.days.lost)
head(top.days.lost, 10)
```
the "American Coal Company New Era Mine" take 5 spots.
Let's take a look at its second quarter of 2005:
```{r new era}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc
    #ai_occ_desc 
    #ai_narr
    ) 
head(new.era)
```
In particular, the top accident was:
```{r new era accident 1}
if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era.top.accidents <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc,
    ai_occ_desc, 
    ai_narr,
    inj_degr_desc
    ) 
print(as.character(new.era.top.accidents$ai_narr[1]))
print(as.character(new.era.top.accidents$inj_degr_desc[1]))
```
and the second to top accident was:
```{r new era, accident 2}
if(!exists("new.era.top.accidents")){
 if(!exists("accidents")){load("./San Antonio/data/secret_ingredients.RData")}
new.era.top.accidents <- accidents %>% 
  filter(mine_id == 1102752 & cal_yr == 2005 & cal_qtr == 2) %>% 
  arrange(desc(days_lost)) %>% 
  select(
    ai_dt, 
    days_lost, 
    ai_class_desc,
    ai_occ_desc, 
    ai_narr
    )  
}
print(as.character(new.era.top.accidents$ai_narr[2]))
print(as.character(new.era.top.accidents$inj_degr_desc[2]))
```

@@

### Lognormal Distribution of Nonzero Days Lost
